Design Document: Monte Carlo Maximum Likelihood for Generalized Linear Mixed Models

### 2015-01-11 NewDesignDoc/DesignDocGLMM.tex
Finished theorem.
About to start editing doc from beginning.

That is, we want to show the existence of the following:
\begin{align}
&\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \label{eq:first} \\
&\int \dfrac{ \left[ \nabla \log f_\theta (u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \label{eq:second} \\
&\int \dfrac{  \nabla \log f_\theta (u)  \nabla \log f_\theta (y|u)  \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \\
\end{align}

First, we start with \eqref{eq:first}:
\begin{align}
\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du 
&=\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{\tilde{f}(u)} du \\
&\leq \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{p_1\grave{f}(u)} du \\
&\propto \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \exp(-u'D^{-1}u)}{p_1\left[ 1+u'u/\zeta  \right]^{-(\zeta+q)/2}} du \\
&= \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \exp(u'D^{-1}u)} du \\
&= \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \label{eq:soon}
\end{align}
By the Cauchy-Schwartz inequality, the integral in \eqref{eq:soon} exists if
\begin{align}
 & \int \dfrac{ \left[\dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \nonumber \\
&\propto  \int \dfrac{ \left[X' c'(\eta) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \label{eq:soon2}
\end{align}
exists, where $c'(\eta)$ is a vector with components $c'(\eta_i)$.  This will converge as long as no term in the numerator of the integrand grows more quickly than $\exp(u'D^{-1}u$. The second and third terms grow less quickly than $\exp(u'D^{-1}u$, so $\left[ c'(\eta)\right]^2$ is the only term to check.  If $y|u \sim$ Bernoulli, then 
\begin{align}
c'(\eta_i)= \dfrac{\exp(\eta_i)}{1+\exp(\eta_i)},
\end{align}
which does not grow more quickly than $\exp(u'D^{-1}u)$. If $y|u \sim$ Poisson, then
\begin{align}
c'(\eta_i)= e^{\eta_i},
\end{align}
which does not grow more quickly than $\exp(u'D^{-1}u)$. Therefore, \eqref{eq:first} exists and is finite, and the variance of 
\begin{align}
\sum_{k=1}^m \nabla \log f_\theta (y|u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)}
\end{align}
is finite.

Next, we move on to showing the existence of \eqref{eq:second}.
EDITED TO HERE.

 That is, we want to show the existence of
\begin{align}
\int \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du.
\end{align}
That is, we want to show the existence of
\begin{align}
\int &\dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du \\
&\leq \int  \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u) + \log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)} du  \\
&\leq  \int \dfrac{N(u|0,D)^2 \left[ \dfrac{\partial}{\partial \beta} \log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2}{p_1 N(u|0,D)} du  \\
&\leq \dfrac{1}{p_1}  \int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du.
\end{align}
By the Cauchy-Schwartz inequality, 
\begin{align}
  &\int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du \\
& \leq \left[  \int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du \right]^{1/2}  \left[  \int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u)   \right]^2 du \right]^{1/2} .
\end{align}
Therefore, I need to show that each of these two integrals is finite.  I will start with the first of the two integrals: 
\begin{align}
\int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta(u)  \right]^2 du. 
\end{align}
Recall the notation from section \ref{sec:Ddiag}.  If
\begin{align}
\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t< \infty 
\end{align}
for every $t=1,...,T$, then
\begin{align}
\int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta(u)  \right]^2 du < \infty
\end{align}
by Cauchy Schwartz.  Therefore, I will prove the integral is finite for the general case of $u_t$ and $\nu_t$. First, we recognize that our integral is actually an expectation of a function of a normal random variable:
\begin{align}
\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t &=
\int \dfrac{1}{\nu_t^{q_t/2}} e^{-u_t'u_t/(2 \nu_t)} \left[ -\dfrac{q_t}{2 \nu_t} + \dfrac{u_t'u_t}{2 \nu_t^2}  \right]^2 du_t .
\end{align}
Normal distributions have finite moments of all orders, so we know that\begin{align}
\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t < \infty.
\end{align}

Next, we want to show 
\begin{align}
\int N(u|0,D) \left[\dfrac{\partial}{\partial \beta} \log f_\theta(y|u)   \right]^2 du < \infty.
\end{align}
 Recall that $\eta=X \beta +Z u$. Letting $\dfrac{\partial}{\partial \eta} c(\eta)=\mu$, we see 
\begin{align}
\int N(u|0,D) \left[\dfrac{\partial}{\partial \beta} \log f_\theta(y|u)   \right]^2 du &= \int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du
%&\propto  \int N(u|0,D) \mu' XX' Y du + \int N(u|0,D) \mu' X X' \mu du   .
\end{align}
We will consider this integral for the cases of $Y|u$ being a Bernoulli and a Poisson random variable. When $Y|u$ is Bernoulli, then $0 \leq \mu \leq 1.$ Therefore,
\begin{align}
\int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du
\end{align}
exists and is finite.
When $Y|u$ is a Poisson random variable, then for any  $\eta$, 
\begin{align}
\dfrac{\partial}{\partial \eta} c(\eta) = e^\eta.
\end{align}
Then
\begin{align}
\int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du &\propto \int N(u|0,D)  e^{\eta} e^{\eta}    du \\
&\propto \int N(u|0,D) e^{2Zu} du 
\end{align}
exists and is finite.

Next, we want to show that 
\begin{align}
\sum_{k=1}^m \nabla \log \tilde{f} (u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)}
\end{align}
 has finite variance. That is, we want to show the existence of
\begin{align}
\int \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du.
\end{align}
We see that
\begin{align}
\int& \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du\\
&\leq  \int \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)} du\\
&= \dfrac{1}{p_1} \int N(u|0,D) \left[\nabla \log \tilde{f}u) \right]^2 du\\
&=\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{p_1 \dfrac{\partial}{\partial \nu} N(u|0,D)}{p_1 N(u|0,D)+p_2 N(u|u^*,D^*)+p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})}   \right]^2 du\\
&\leq\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{p_1 \dfrac{\partial}{\partial \nu} N(u|0,D)}{p_1 N(u|0,D)}   \right]^2 du\\
&=\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{ \dfrac{\partial}{\partial \nu} N(u|0,D)}{ N(u|0,D)}   \right]^2 du\\
&= \dfrac{1}{p_1} \int \dfrac{\left[ \dfrac{\partial}{\partial \nu} N(u|0,D)  \right]^2}{N(u|0,D)} du \\
\end{align}
Now we use
\begin{align}
\dfrac{\partial}{\partial \nu} \log N(u|0,D) = \dfrac{\dfrac{\partial}{\partial \nu}  N(u|0,D)}{N(u|0,D)}
\end{align}
to see
\begin{align}
 \dfrac{1}{p_1} \int \dfrac{\left[ \dfrac{\partial}{\partial \nu} N(u|0,D)  \right]^2}{N(u|0,D)} du &=\dfrac{1}{p_1} \int  N(u|0,D) \left[ \dfrac{\partial}{\partial \nu} \log N(u|0,D)  \right]^2 du \\
&= \dfrac{1}{p_1} \int  N(u|0,D) \left[ \dfrac{\partial}{\partial \nu} \log N(u|0,D)  \right]^2 du 
\end{align}
which exists and is finite.

Therefore, it is proven that 
\begin{align}
\int \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du 
\end{align}
exists and is finite. Therefore, since  the gradient of the MCLA has finite variance, we can conclude the gradient of the MCLA has a Central Limit Theorem.

>>>>

That is, we want to show the existence of the following:
\begin{align}
&\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \label{eq:first} \\
&\int \dfrac{ \left[ \nabla \log f_\theta (u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \label{eq:second} \\
&\int \dfrac{  \nabla \log f_\theta (u)  \nabla \log f_\theta (y|u)  \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du \label{eq:third} 
\end{align}

First, we start with \eqref{eq:first}:
\begin{align}
\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du 
&=\int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{\tilde{f}(u)} du \\
&\leq \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{p_1\grave{f}(u)} du \\
&\propto \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \exp(-u'D^{-1}u)}{p_1\left[ 1+u'u/\zeta  \right]^{-(\zeta+q)/2}} du \\
&= \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \left[ f_\theta(y|u)\right]^2 \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \exp(u'D^{-1}u)} du \\
&= \int \dfrac{ \left[ \nabla \log f_\theta (y|u) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \label{eq:soon}
\end{align}
By the Cauchy-Schwartz inequality, the integral in \eqref{eq:soon} exists if
\begin{align}
 & \int \dfrac{ \left[\dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \nonumber \\
&\propto  \int \dfrac{ \left[X' c'(\eta) \right]^2 \, \exp(2y'(X \beta+Zu)) \,  \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{ p_1 \, \exp(2 c(\eta)) \,\exp(u'D^{-1}u)} du \label{eq:soon2}
\end{align}
exists, where $c'(\eta)$ is a vector with components $c'(\eta_i)$.  This will converge as long as no term in the numerator of the integrand grows more quickly than $\exp(u'D^{-1}u$. The second and third terms grow less quickly than $\exp(u'D^{-1}u$, so $\left[ c'(\eta)\right]^2$ is the only term to check.  If $y|u \sim$ Bernoulli, then 
\begin{align}
c'(\eta_i)= \dfrac{\exp(\eta_i)}{1+\exp(\eta_i)},
\end{align}
which does not grow more quickly than $\exp(u'D^{-1}u)$. If $y|u \sim$ Poisson, then
\begin{align}
c'(\eta_i)= e^{\eta_i},
\end{align}
which does not grow more quickly than $\exp(u'D^{-1}u)$. Therefore, \eqref{eq:first} exists and is finite, and 
\begin{align}
\var \left( \sum_{k=1}^m \nabla \log f_\theta (y|u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)} \right) < \infty.
\end{align}
is finite.

Next, we move on to showing the existence of \eqref{eq:second}.
\begin{align}
\int \dfrac{ \left[ \nabla \log f_\theta (u) \right]^2 \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du &= 
\int \dfrac{ \left[ \nabla \log f_\theta (u) \right]^2 \left[ f_\theta(y|u)\right]^2  \left[ f_\theta(u)\right]^2}{\tilde{f}(u)} du\\
&\leq \int \dfrac{ \left[ \nabla \log f_\theta (u) \right]^2 \left[ f_\theta(y|u)\right]^2  \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du
\end{align}
By the Cauchy-Schwartz inequality, the above integral exists as long as  
\begin{align}
\int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t} \log f_\theta (u) \right]^2 \left[ f_\theta(y|u)\right]^2  \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du < \infty
\end{align}
for every $t=1,\ldots, T$. We see
\begin{align}
&\int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t} \log f_\theta (u) \right]^2 \left[ f_\theta(y|u)\right]^2  \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du \\
&= \int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t} \log f_\theta (u) \right]^2 \exp(2y'(X\beta+Zu)   )  \left[ f_\theta(u)\right]^2}{p_1 \exp(2c(\eta))    \grave{f}(u)} du \\
&\propto \int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t} \log f_\theta (u) \right]^2 \exp(2y'(X\beta+Zu)   ) \,   \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \exp(2c(\eta)) \, \exp(u'D^{-1}u)  } du\\
&= \int \dfrac{ \left[  -\dfrac{q_t}{2 \nu_t} + \dfrac{u_t'u_t}{2 \nu_t^2}   \right]^2 \exp(2y'(X\beta+Zu)   ) \,   \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \exp(2c(\eta)) \, \exp(u'D^{-1}u)  } du
\end{align}
Because every term in the numerator of the integrand grows less quickly than $\exp(u'D^{-1}u)$, the integral exists.  Therefore, \eqref{eq:second} exists and 
\begin{align}
\var \left(\sum_{k=1}^m \nabla \log f_\theta (u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)} \right) < \infty.
\end{align}

Lastly, we want to show the existence of \eqref{eq:third}. We see
\begin{align}
\int \dfrac{  \nabla \log f_\theta (u)\,  \nabla \log f_\theta (y|u) \, \left[ f_\theta(u,y)\right]^2}{\tilde{f}(u)} du &=
\int \dfrac{  \nabla \log f_\theta (u) \, \nabla \log f_\theta (y|u) \, \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{\tilde{f}(u)} du \\
&\leq
\int \dfrac{  \nabla \log f_\theta (u) \,  \nabla \log f_\theta (y|u)\,  \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du \label{eq:this1}
\end{align}
Again, we use the Cauchy-Schwartz inequality to check the existence of \eqref{eq:this1}. If, for every $t=1,\ldots,T$,
\begin{align}
\int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t}  \log f_\theta (u) \right] \left[  \dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]   \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du \label{eq:this1}
\end{align}
exists, then \eqref{eq:this1} also exists. Continuing, we see
\begin{align}
& \int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t}  \log f_\theta (u) \right] \left[  \dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]   \left[ f_\theta(y|u)\right]^2 \left[ f_\theta(u)\right]^2}{p_1 \grave{f}(u)} du\\
 &\propto \int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t}  \log f_\theta (u) \right] \left[  \dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]   \left[ f_\theta(y|u)\right]^2 }{p_1 \, \exp(u'D^{-1}u) \, \grave{f}(u)} du\\
 &\propto \int \dfrac{ \left[ \dfrac{\partial}{\partial \nu_t}  \log f_\theta (u) \right] \left[  \dfrac{\partial}{\partial \beta} \log f_\theta (y|u) \right]   \left[ f_\theta(y|u)\right]^2 \, \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \, \exp(u'D^{-1}u) } du\\
&\propto \int \dfrac{ \left[      -\dfrac{q_t}{2 \nu_t} + \dfrac{u_t'u_t}{2 \nu_t^2}        \right] \left[  X'(y-c'(\eta)) \right]   \left[ f_\theta(y|u)\right]^2 \, \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \, \exp(u'D^{-1}u) } du\\
&= \int \dfrac{ \left[      -\dfrac{q_t}{2 \nu_t} + \dfrac{u_t'u_t}{2 \nu_t^2}        \right] \left[  X'(y-c'(\eta)) \right]   \, \exp(2y'(X\beta+Zu)) \, \left[ 1+u'u/\zeta  \right]^{(\zeta+q)/2} }{p_1 \, \exp(u'D^{-1}u) \, \exp(2 c(\eta)) } du. \label{eq:this2}
\end{align}
We have already shown that $-c'(\eta)$ does not grow more quickly than $\exp(u'D^{-1}u)$. The other terms in the numerator of the integrand shown in \eqref{eq:this2} also grow more slowly than $\exp(u'D^{-1}u)$. We conclude that \eqref{eq:this2} exists, which implies that \eqref{eq:third} exists and
\begin{align}
\cov \left(\sum_{k=1}^m \nabla \log f_\theta (y|u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)} \, , \, \sum_{k=1}^m \nabla \log f_\theta (u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)} \right) < \infty.
\end{align}
This shows that
\begin{align}
\var \left( \sum_{k=1}^m     \nabla \log f_\theta(u_k,y)\dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)} \right) < \infty. 
\end{align}
Therefore, the gradient of the MCLA has finite variance and a central limit theorem.

%EDITED TO HERE.
%
% That is, we want to show the existence of
%\int \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du.
%That is, we want to show the existence of
%\int &\dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du \\
%&\leq \int  \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u) + \log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)} du  \\
%&\leq  \int \dfrac{N(u|0,D)^2 \left[ \dfrac{\partial}{\partial \beta} \log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2}{p_1 N(u|0,D)} du  \\
%&\leq \dfrac{1}{p_1}  \int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du.
%By the Cauchy-Schwartz inequality, 
%  &\int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u) \, \, \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du \\
%& \leq \left[  \int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta (u)  \right]^2 du \right]^{1/2}  \left[  \int N(u|0,D) \left[ \dfrac{\partial}{\partial \beta}\log f_\theta(y|u)   \right]^2 du \right]^{1/2} .
%Therefore, I need to show that each of these two integrals is finite.  I will start with the first of the two integrals: 
%\int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta(u)  \right]^2 du. 
%Recall the notation from section \ref{sec:Ddiag}.  If
%\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t< \infty 
%for every $t=1,...,T$, then
%\int N(u|0,D) \left[  \dfrac{\partial}{\partial \nu} \log f_\theta(u)  \right]^2 du < \infty
%by Cauchy Schwartz.  Therefore, I will prove the integral is finite for the general case of $u_t$ and $\nu_t$. First, we recognize that our integral is actually an expectation of a function of a normal random variable:
%\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t &=
%\int \dfrac{1}{\nu_t^{q_t/2}} e^{-u_t'u_t/(2 \nu_t)} \left[ -\dfrac{q_t}{2 \nu_t} + \dfrac{u_t'u_t}{2 \nu_t^2}  \right]^2 du_t .
%Normal distributions have finite moments of all orders, so we know that\begin{align}
%\int N(u_t|0,D_t) \left[  \dfrac{\partial}{\partial \nu_t} \log f_\theta(u)  \right]^2 du_t < \infty.
%
%
%
%
%Next, we want to show 
%\int N(u|0,D) \left[\dfrac{\partial}{\partial \beta} \log f_\theta(y|u)   \right]^2 du < \infty.
% Recall that $\eta=X \beta +Z u$. Letting $\dfrac{\partial}{\partial \eta} c(\eta)=\mu$, we see 
%\int N(u|0,D) \left[\dfrac{\partial}{\partial \beta} \log f_\theta(y|u)   \right]^2 du &= \int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du
%%&\propto  \int N(u|0,D) \mu' XX' Y du + \int N(u|0,D) \mu' X X' \mu du   .
%We will consider this integral for the cases of $Y|u$ being a Bernoulli and a Poisson random variable. When $Y|u$ is Bernoulli, then $0 \leq \mu \leq 1.$ Therefore,
%\int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du
%exists and is finite.
%When $Y|u$ is a Poisson random variable, then for any  $\eta$, 
%\dfrac{\partial}{\partial \eta} c(\eta) = e^\eta.
%Then
%\int N(u|0,D) \left[ (Y'- \mu') X X'(Y- \mu)   \right] du &\propto \int N(u|0,D)  e^{\eta} e^{\eta}    du \\
%&\propto \int N(u|0,D) e^{2Zu} du 
%exists and is finite.
%
%Next, we want to show that 
%\sum_{k=1}^m \nabla \log \tilde{f} (u_k) \dfrac{f_\theta(u_k,y)}{\tilde{f}(u_k)}
% has finite variance. That is, we want to show the existence of
%\int \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du.
%We see that
%\int& \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du\\
%&\leq  \int \dfrac{N(u|0,D)^2 \left[\nabla \log \tilde{f}u) \right]^2}{p_1 N(u|0,D)} du\\
%&= \dfrac{1}{p_1} \int N(u|0,D) \left[\nabla \log \tilde{f}u) \right]^2 du\\
%&=\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{p_1 \dfrac{\partial}{\partial \nu} N(u|0,D)}{p_1 N(u|0,D)+p_2 N(u|u^*,D^*)+p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})}   \right]^2 du\\
%&\leq\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{p_1 \dfrac{\partial}{\partial \nu} N(u|0,D)}{p_1 N(u|0,D)}   \right]^2 du\\
%&=\dfrac{1}{p_1} \int N(u|0,D) \left[  \dfrac{ \dfrac{\partial}{\partial \nu} N(u|0,D)}{ N(u|0,D)}   \right]^2 du\\
%&= \dfrac{1}{p_1} \int \dfrac{\left[ \dfrac{\partial}{\partial \nu} N(u|0,D)  \right]^2}{N(u|0,D)} du \\
%Now we use
%\dfrac{\partial}{\partial \nu} \log N(u|0,D) = \dfrac{\dfrac{\partial}{\partial \nu}  N(u|0,D)}{N(u|0,D)}
%to see
% \dfrac{1}{p_1} \int \dfrac{\left[ \dfrac{\partial}{\partial \nu} N(u|0,D)  \right]^2}{N(u|0,D)} du &=\dfrac{1}{p_1} \int  N(u|0,D) \left[ \dfrac{\partial}{\partial \nu} \log N(u|0,D)  \right]^2 du \\
%&= \dfrac{1}{p_1} \int  N(u|0,D) \left[ \dfrac{\partial}{\partial \nu} \log N(u|0,D)  \right]^2 du 
%which exists and is finite.
%
%
%
%Therefore, it is proven that 
%\int \dfrac{N(u|0,D)^2 \left[\nabla \left(\log f_\theta(y|u)+\log f_\theta (u) \right) \right]^2}{p_1 N(u|0,D)+p_2 N(u|u^*, D^*) + p_3 N(u|u^*, ((Z'  c''(X \beta^*+Zu^*) Z +(D^*)^{-1}   )^{-1})} du 
%exists and is finite. Therefore, since  the gradient of the MCLA has finite variance, we can conclude the gradient of the MCLA has a Central Limit Theorem.
